Exploring mathematical objects from custom-tailored mathematical universes

### 2020-01-16 paper-filmat.tex
to do

* use the phrase "very rich and very deep" (or similarly) about set theory
* PA doesn't have models
* Sven(?)
* semantic view vs. syntactic view
* Kripke models
* more pointers to topos literature
* Reference for the effective topos
* Reference idempotency
* A topos is more than its semantics
* Reference: Moerdijk
* Check references everywhere (give good pointers)
* Format rules in a better way
* Format examples in Eff in a better way

>>>>

* use the phrase "very rich and very deep" (or similarly) about set theory
* PA doesn't have models
* Sven(?)
* semantic view vs. syntactic view
* Kripke models
* more pointers to topos literature
* Reference for the effective topos
* Reference idempotency
* A topos is more than its semantics
* Reference: Moerdijk
* Check references everywhere (give good pointers)
* Format rules in a better way
* Format examples in Eff in a better way
* toposes are not small (Figure 1)
